Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/methodology.tex

To ensure that participants had read and understood this device's capabilities, since it would form the basis for many of our survey questions, we ask them two multiple-choice comprehension questions about the device's capabilities and where it might be worn. We filtered out those who could not answer these questions.

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}. We randomly presented each participant with 2 of these 5 questions: 
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item How would you feel if an app on your <device> vibrated your phone without asking you first?
\item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
\item How would you feel if an app on your <device> un-muted a phone call without asking you first?
\item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?
\end{enumerate}

In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these five questions were among the pool of 293 questions from which participants were randomly assigned 6). In this section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).

>>>>

To ensure that participants had read and understood this device's capabilities, since it would form the basis for many of our survey questions, we ask them two multiple-choice comprehension questions about the device's capabilities and where it might be worn. We filtered out responses from participants who could not answer these questions.

@@

\subsubsection{Smartphone Scenarios}
\label{sec:smartphones}
We presented participants with a second set of scenarios to control for the type of device being used. Rather than using the previous pool of 288 <data> and <recipient> combinations, we selected 5 scenarios that Felt \etal found least and most concerning to their participants~\cite{Felt}:
\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
\item How would you feel if an app on your <device> vibrated your phone without asking you first?
\item How would you feel if an app on your <device> connected to a Bluetooth device (like a headset) without asking you first?
\item How would you feel if an app on your <device> un-muted a phone call without asking you first?
\item How would you feel if an app on your <device> took screenshots when you were using other apps, without asking you first?
\item How would you feel if an app on your <device> sent premium (they cost money) calls or text messages, without asking you first?
\end{enumerate}

In the previously described section of our survey, <device> was set to ``Cubetastic3000'' and not every participant received one of these questions (i.e., these 5 questions were among the pool of 293 questions from which participants were randomly assigned 6). In the separate smartphone section of the survey, every participant received exactly two of these questions, where <device> was set to ``smartphone.'' This allowed us to perform controlled comparisons based on whether the same misbehavior was occurring on a smartphone (i.e., a better understood device) or the Cubetastic3000 (i.e., a fictitious wearable device).
